Demes: a standard format for demographic models

### 2022-06-08 paper.tex
Linkify urls.
Also Americanize software-table.tex.
Added MH grant info

@@

>>>>

% Import this last to avoid mysterious errors.
\usepackage[implicit=false]{hyperref}

@@

\section*{Acknowledgments}
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst was supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
